analysis-pilot

### 2023-07-19 code/analysis-pilot.Rmd
data cleaning initial

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(jsonlite)

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}

pilot_start=lubridate::ymd('2023-7-07') 
pilot_end=lubridate::ymd('2023-7-11')
```

```{r}
raw_data <- read.csv(here("data/rounds7.19.csv"), header = TRUE) %>% 
  filter(createdAt >= pilot_start) %>%
  filter(createdAt <= pilot_end) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  select(-chat) |> 
  pivot_longer(cols=starts_with('player'), names_to=c("playerId", "info"), names_prefix="player_", names_sep="_",
               values_to="values", values_transform=as.character, values_drop_na=T) %>% 
  filter(values!="") %>% 
  filter(playerId!=speaker) %>% 
  pivot_wider(names_from=info, values_from=values)

  write_csv(here(data_location, 'raw_results.csv'))
```
